---
title: "US_Mil_Aid_Rec_St_Coop"
author: "Daniel Shapiro"
date: "1/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(readr)
library(readxl)
library(stringr)
library(data.table)
library(stats)
```

## INDEPENDENT VARIABLE

# Data read-in

```{r data readin}
load("Dataset-Military-Aid-and-Recipient-State-Cooperation-091310 (4).RData")
x <- as_data_frame(x)

import <- read_csv("TIV-Import-All-2000-2019.csv", col_types = cols(
  .default = col_double(),
  Country = col_character()
))

usa <- read_csv("TIV-Export-USA-2000-2019.csv", col_types = cols(
  .default = col_double(),
  Country = col_character()
))

russia <- read_csv("TIV-Export-RUS-2000-2019.csv", col_types = cols(
  .default = col_double(),
  Country = col_character()
))

russia <- russia[-92, ]
usa <- usa[-130, ]
import <- import[-201, ]

russia <- russia %>% pivot_longer(`2000`:`2019`, names_to = "Year", values_to = "Russia") %>%
  select(-Total)

usa <- usa %>% pivot_longer(`2000`:`2019`, names_to = "Year", values_to = "USA") %>%
  select(-Total)

import <- import %>% pivot_longer(`2000`:`2019`, names_to = "Year", values_to = "Full") %>%
  select(-Total)

data <- merge(russia, usa, by = c("Country", "Year"), all = TRUE)
data[is.na(data)] <- 0

fulldata <- merge(data, import, by = c("Country", "Year"), all = TRUE)
fulldata[is.na(fulldata)] <- 0

# Full data column setup

fulldata <- fulldata %>% 
  mutate(RussiaPct = Russia/Full*100) %>%
  mutate(USPct = USA/Full*100)
fulldata[is.na(fulldata)] <- 0
```

# Finding Countries in Last 10 years with Presence of Both Russia and USA, then 2002-2010

```{r}
recent <- fulldata %>%
  filter(Year %in% c("2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019"))  %>%
  filter(RussiaPct >= 2) %>%
  filter(USPct >= 2)
```

```{r}
recent <- recent[-c(72:81), ]
```

```{r}
recent
```

# Historic with linear regression

```{r}
historic <- fulldata %>%
  filter(Year %in% c("2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010"))

historic$Year = as.numeric(as.character(historic$Year))

# A LOT of basic linear regressions. I went through the data table, took a regression for each country that Russia sold to, looked at the slopes, and kept the ones that were positive. I then removed the ones from this list that the U.S. did not sell any weapons to during this period (Armenia, Croatia, Cyprus, Kenya, Libya, Mongolia, Senegal, Slovenia, Syria, Tajikistan, Turkmenistan, Uzbekistan, Vietnam).

Afghanistan <- historic[1:9, ]
lm(data = Afghanistan, formula = Russia ~ Year)
Algeria <- historic[28:36, ]
lm(data = Algeria, formula = Russia ~ Year)
Azerbaijan <- historic[82:90, ]
lm(data = Azerbaijan, formula = Russia ~ Year)
Brazil <- historic[190:198, ]
lm(data = Brazil, formula = Russia ~ Year)
Chad <- historic[280:288, ]
lm(data = Chad, formula = Russia ~ Year)
Ecuador <- historic[433:441, ]
lm(data = Ecuador, formula = Russia ~ Year)
Egypt <- historic[442:450, ]
lm(data = Egypt, formula = Russia ~ Year)
India <- historic[667:675, ]
lm(data = India, formula = Russia ~ Year)
Indonesia <- historic[676:684, ]
lm(data = Indonesia, formula = Russia ~ Year)
Iraq <- historic[694:702, ]
lm(data = Iraq, formula = Russia ~ Year)
Jordan <- historic[748:756, ]
lm(data = Jordan, formula = Russia ~ Year)
Kazakhstan <- historic[757:765, ]
lm(data = Kazakhstan, formula = Russia ~ Year)
Kuwait <- historic[784:792, ]
lm(data = Kuwait, formula = Russia ~ Year)
Malaysia <- historic[937:945, ]
lm(data = Malaysia, formula = Russia ~ Year)
Mexico <- historic[991:999, ]
lm(data = Mexico, formula = Russia ~ Year)
Morocco <- historic[1018:1026, ]
lm(data = Morocco, formula = Russia ~ Year)
Nicaragua <- historic[1090:1098, ]
lm(data = Nicaragua, formula = Russia ~ Year)
Niger <- historic[1099:1107, ]
lm(data = Niger, formula = Russia ~ Year)
Peru <- historic[1225:1233, ]
lm(data = Peru, formula = Russia ~ Year)
Poland <- historic[1261:1269, ]
lm(data = Poland, formula = Russia ~ Year)
Thailand <- historic[1549:1557, ]
lm(data = Thailand, formula = Russia ~ Year)
Turkey <- historic[1612:1620, ]
lm(data = Turkey, formula = Russia ~ Year)
UAE <- historic[1639:1647, ]
lm(data = UAE, formula = Russia ~ Year)
Venezuela <- historic[1756:1764, ]
lm(data = Venezuela, formula = Russia ~ Year)
```

# Filtering Countries from previous category into U.S. aid data (dataframe x); writing to new CSV for further use in Excel

```{r}
specific <- x %>% filter(ccodesrc %in% c(692, 771, 140, 651, 750, 645, 663, 690, 475, 770, 135, 800, 640, 696, 704))

specific <- specific[ ,1:19]

write.csv(specific, "specific.csv", row.names = FALSE)
```

## DEPENDENT VARIABLE

# Reading in and messing with DCAD data

```{r}
dcadmain <- read_csv("DCAD-v1.0-main.csv", col_types = cols(
  .default = col_double(),
  cowName1 = col_character(),
  cowName2 = col_character(),
  type = col_character(),
  category1 = col_character(),
  category2 = col_character(),
  category3 = col_character(),
  categoryConf = col_character(),
  fullText = col_character(),
  sourceType = col_character(),
  source = col_character(),
  DCAid = col_character()
)) %>%
  filter(cowName1 %in% c("USA", "RUS"))
```

```{r}
dyadic <- read_csv("DCAD-v1.0-dyadic.csv", col_types = cols(
  ccode1 = col_double(),
  abbrev1 = col_character(),
  ccode2 = col_double(),
  abbrev2 = col_character(),
  year = col_double(),
  dcaGeneralV1 = col_double(),
  dcaGeneralV2 = col_double(),
  dcaSectorV1 = col_double(),
  dcaSectorV2 = col_double(),
  dcaAnyV1 = col_double(),
  dcaAnyV2 = col_double()
)) %>%
  filter(year %in% c(2002:2010)) %>%
  filter(abbrev1 == "USA") %>%
  dplyr::select(c(abbrev1, abbrev2, year, dcaAnyV1, dcaAnyV2)) %>%
  
# Separating into the countries that we got through the independent variable
  
  filter(abbrev2 %in% c("MEX", "NIC", "VEN", "ECU", "PER", "BRA", "POL", "AZE", "NIR", "CHA", "ALG", "MOR", "TUR", "IRQ", "EGY", "JOR", "KUW", "UAE", "AFG", "KZK", "IND", "THI", "MAL", "INS")) %>%
  filter(year %in% c("2002", "2010"))
```

# Logistic Regression

```{r}
mylogit <- glm(data = dyadic, formula = dcaAnyV1 ~ year, family = "binomial")
summary(mylogit)

# Coefficients don't look great...
```

# ADDITIONAL 

# Opening and Reading in Polity V Scores

```{r}
polity <- read_xls("p5v2018.xls") 
```

```{r}
polity <- polity %>%
  filter(year %in% c("1990", "1991", "1992", "1993", "1994", "1995", "1996", "1997", "1998", "1999", "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018")) %>%
  filter(country %in% c("Peru", "Brazil", "Nigeria", "Turkey", "Iraq", "Egypt", "Jordan", "Kuwait", "Bahrain", "UAE", "Uzbekistan", "India", "Pakistan", "Bangladesh", "Thailand")) %>%
  select(c(country, year, polity2))

write.csv(polity, "polity.csv", row.names = FALSE)
```